---
title: "Developing Data Products Week 2 Assignment"
output: html_document
name: Kimberly Yuen
date: October 25 2023
---

## Introduction

Instructions: 
Create a web page using R Markdown that features a map created with Leaflet. 

Host your webpage on either GitHub Pages, RPubs, or NeoCities.

Your webpage must contain the date that you created the document, and it must contain a map created with Leaflet. We would love to see you show off your creativity! 

I will create an interactive map of my top 5 Asian restaurants in Stockholm, Sweden.

## Load data

```{r}
library(leaflet)
restaurants<-data.frame(lat=c(59.31832265376712,59.332982854383786,59.34778201788994,59.340709858423516,59.313661778540045),lng=c(18.053591602065683,18.047128029334733,18.066917468119044,18.041738941424036,18.08569378976499),name=c("Lao Lao","Eat East","Hao Kök","Minh Mat","Mormors Restaurang & Dumplings"))
```

## Plot map
Plotting my Top 5 Asian restaurants in Stockholm.

```{r}
my_map<- restaurants %>% leaflet() %>% addTiles() %>% addMarkers(popup =restaurants$name,clusterOptions = markerClusterOptions())
my_map
```

