---
title: "Developing Data Products Week 3 Assignment"
output: html_document
date: October 25 2023
---

## Introduction

Instructions: 
Create a web page presentation using R Markdown that features a plot created with Plotly. Host your webpage on either GitHub Pages, RPubs, or NeoCities. Your webpage must contain the date that you created the document, and it must contain a plot created with Plotly. We would love to see you show off your creativity! 

I will create a scatterplot using the mtcars data set of Miles/gallon (mpg) vs Gross horsepower (hp) using colors to show automatic and manual transmission.

## Load/prepare data
Load plotly package.
Re-code Transmission variable (am) into "automatic" (0) and "manual" (1).
```{r}
library(plotly)
mtcars$am <- gsub("0", "auto", mtcars$am)
mtcars$am <- gsub("1", "manual", mtcars$am)
```

## Plot scatterplot 
Plotting scatterplot of mpg vs hp with automatic transmissions in blue and manual transmissions in green.

```{r}
plot_ly(mtcars, x = ~hp, y = ~mpg, type = "scatter",split = ~am)
```